{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-05-29 Notebook LaTEX/Momentum Accelerations/main.tex
>w< mbp, added new

        \begin{theorem}[Convergence Rate of PPM]
            The convergence rate of PPM applied to $f$, closed, convex proper, we have convergence rate of the function value: 
            $$
            f(x_T) - f(x_*) \le O\left(\left(\sum_{i=1}^{T}\eta_t\right)^{-1}\right). 
            $$
            Where $x_*$ is the minimizer of $f$. 
        \end{theorem}
        \begin{proof}
            With $\Delta_t = f(x_t) - f(x_*), \Upsilon_t = \sum_{i = 1}^{t}\eta_i$ so $\Phi_t = \Upsilon_t\Delta_t + \frac{1}{2}\Vert x_t - x_*\Vert^2$ by consider $u = x_*$, invoking previous theorem and do
            \begin{align*}
                \Upsilon_T\Delta_T \le \Phi_T 
                &\le 
                \Phi_0 = \frac{1}{2}\Vert x_0 - x_*\Vert^2 
                \\
                \implies \Delta_T 
                &\le 
                \frac{1}{2\Upsilon_T} \Vert x_0 - x_*\Vert^2. 
            \end{align*}
            Hence, the convergence rate of PPM for all convex function is the above. 
        \end{proof}
        \begin{remark}
            The analysis of the above is taken from (REFERENCE NEEDED). 
        \end{remark}
\section{Application of the Proximal Point Method}
    The PPM method and the Lyaounov function derived above serves as tamplate for other algorithms. 
    In optimizations, people uses lower and upper approximation of the objective function to approximate the PPM. 
    Such an approach involves a diverse range of algorithms, including second order algorithms such as Newton's method. 
    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by an lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
    \begin{align}
        l_f(x| \bar x) 
        \le f(x) \le l_f(x|\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
    \end{align}
    The above characterization is generic enough to include the case where $l_f(x|\bar x)$ under approximates function that is non-smooth. 
    To make use of the theorems discussed previously, we assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$. 
    \par 
    The approximated proximal point method is applying PPM to the function $l_f(x|x_t)$ for each iteration, i.e: $x_{t +1} = \hprox_{\eta_{t + 1}}[u\mapsto l_f(u | x_t)](x_t)$.

>>>>

        \begin{theorem}[Convergence Rate of PPM]
            The convergence rate of PPM applied to $f$, closed, convex proper, we have convergence rate of the function value: 
            $$
            f(x_T) - f(x_*) \le O\left(\left(\sum_{i=1}^{T}\eta_t\right)^{-1}\right). 
            $$
            Where $x_*$ is the minimizer of $f$. 
        \end{theorem}
        \begin{proof}
            With $\Delta_t = f(x_t) - f(x_*), \Upsilon_t = \sum_{i = 1}^{t}\eta_i$ so $\Phi_t = \Upsilon_t\Delta_t + \frac{1}{2}\Vert x_t - x_*\Vert^2$ by consider $u = x_*$, invoking previous theorem and do
            \begin{align*}
                \Upsilon_T\Delta_T \le \Phi_T 
                &\le 
                \Phi_0 = \frac{1}{2}\Vert x_0 - x_*\Vert^2 
                \\
                \implies \Delta_T 
                &\le 
                \frac{1}{2\Upsilon_T} \Vert x_0 - x_*\Vert^2. 
            \end{align*}
            Hence, the convergence rate of PPM for all convex function is the above. 
        \end{proof}
        \begin{remark}
            The analysis of the above is taken from (REFERENCE NEEDED). 
        \end{remark}
        However, the convergence rate of the algorithm can be faster for the same choice of the sequence $(\eta_t)_{t \in \NN}$. 
        \begin{theorem}[Convergence Rate of PPM (Strongly Convex)]

        \end{theorem}
\section{Application of the Proximal Point Method}
    The PPM method and the Lyaounov function derived above serves as tamplate for other algorithms. 
    In optimizations, people uses lower and upper approximation of the objective function to approximate the PPM. 
    Such an approach involves a diverse range of algorithms, including second order algorithms such as Newton's method. 
    To demonstrate, assume that $f$ is a lsc convex function such that it can be approximated by an lower bounding function $l_f(x|\bar x)$ at $\bar x$ such that it satisfies for all $x$: 
    \begin{align}
        l_f(x| \bar x) 
        \le f(x) \le l_f(x|\bar x) + \frac{L}{2}\Vert x - \bar x\Vert^2. 
    \end{align}
    The above characterization is generic enough to include the case where $l_f(x|\bar x)$ under approximates function that is non-smooth. 
    To make use of the theorems discussed previously, we assume that $l_f(x|\bar x)$ is convex for all $x$, at all $\bar x$. 
    \par 
    The approximated proximal point method is applying PPM to the function $l_f(x|x_t)$ for each iteration, i.e: $x_{t +1} = \hprox_{\eta_{t + 1}}[u\mapsto l_f(u | x_t)](x_t)$.

    \begin{theorem}[Convergence of Approximated PPM]\label{thm:lower_approx_ppm_convergence}
        With $f$ be a function that has minimizer: $x_*$; $l_f(x; x_t)$ be a convex, lsc, proper lower-bounding function then the lower-bounding $\phi$ function satisfies inequality: 
        $$
        \phi_t(x) \le \eta_{t + 1}f(x) \le \phi_t(x) + \frac{L\eta_{n + 1}}{2}\Vert x - x_t\Vert^2 \quad \forall x \in \RR^n, 
        $$ 
        Assume an algorithm the makes: 
        $$
        \begin{aligned}
            x_{t +1} = \argmin_{x} \left\lbrace
                l_f(x; x_t) + \frac{1}{2\eta_{t + 1}}\Vert x - x_t\Vert^2
            \right\rbrace, 
        \end{aligned}
        $$
        Then the iterates satisfies: 
        $$
        \begin{aligned}
            \eta_{t + 1}(f(x_{t + 1}) - f(x_*)) + \frac{1}{2}\Vert x_* - x_{t + 1}\Vert^2
            - \frac{1}{2}\Vert x_* - x_t\Vert 
            & \le 
            \left(
                \frac{L \eta_{n + 1}}{2} - \frac{1}{2}
            \right)\Vert x_{t + 1} - x_t\Vert^2.
        \end{aligned}
        $$
    \end{theorem}
    \begin{proof}

    \end{proof}
